---
title: "Trabajo Practico 7 - Parte A - Continuación"
output: html_notebook
---

Clasificador Aleatorio

```{r}
# For manipulating the datasets
library(readr)
# Matrix
library(dplyr) 


# Add probability column

probability_col <- function(dataframe){
  # Random probability
  probabilities <- runif(nrow(dataframe), min=0, max=1) # rnorm!
  # New column
  dataframe$prediction_prob <- probabilities
  return(dataframe)
}

# Load dataset 
trees <- read_csv("/home/emiliano/ia-uncuyo-2021/tp7-ml/data/arbolado-mza-dataset.csv")
trees <- probability_col(trees)

```

Función random_classifier

```{r}
random_classifier <- function(dataframe){
  return(dataframe %>% mutate(prediction_class = ifelse(prediction_prob > 0.5, 1 ,0)))
}

new_dataframe <- read_csv("/home/emiliano/ia-uncuyo-2021/tp7-ml/data/arbolado-publico-mendoza-2021-valid.csv")
with_probability <- probability_col(new_dataframe)
to_validate <- random_classifier(with_probability)
```

Cálculo matriz de confusión - random_classifier

```{r}
matrix_conf <- function(dataf){
  true_positive <- dataf %>% filter(inclinacion_peligrosa == 1 & prediction_class == 1)
  false_positive <- dataf %>% filter(inclinacion_peligrosa == 1 & prediction_class == 0)
  false_negative <- dataf %>% filter(inclinacion_peligrosa == 0 & prediction_class == 1)
  true_negative <- dataf %>% filter(inclinacion_peligrosa == 0 & prediction_class == 0)
  
  return(c(nrow(true_positive), nrow(false_positive), nrow(true_negative),  nrow(false_negative)))
}

mat <- matrix_conf(to_validate)
mat #TP, FP, FN, TN
```

Clasificador por clase mayoritaria

```{r}
biggerclass_classifier <- function(dataframe) {
  majority_count <- dataframe %>% group_by(inclinacion_peligrosa) %>% summarise(total=n())
  print(majority_count)
  if (majority_count[1,"total"] > majority_count[2,"total"]){
    value <- 0
  }
  else{
    value <- 1
  }
  return(dataframe %>% mutate(prediction_class=value))
}

majority <- biggerclass_classifier(with_probability)
#matrix <- confusionMatrix()
mat2 <- matrix_conf(majority)
mat2 #TP, FP, FN, TN
```

Métricas

```{r}
metrics <- function(conf_mat){
  sensitivity <- conf_mat[1] / (conf_mat[1] + conf_mat[2])
  specificity <- conf_mat[4] / (conf_mat[4] + conf_mat[3])
  precision <- conf_mat[1] / (conf_mat[1] + conf_mat[3])
  accuracy <- (conf_mat[1] + conf_mat[4]) / (conf_mat[1] + conf_mat[4] + conf_mat[2] + conf_mat[3])
  return(c(sensitivity, specificity, precision, accuracy))
}

random <- metrics(mat)
random
major <- metrics(mat2)
major
```

Validación cruzada

```{r}
library(rpart)

create_folds <- function(dataframe, n){
  rows = nrow(dataframe)
  data_partition <- ceiling(rows/n)
  datasplit <- split(dataframe, sample(rep(1:n, data_partition))) #return list
  print(datasplit)
  return(datasplit)
}

cross_validation <- function(dataframe, n){

  folds <- create_folds(dataframe, n)
  train_formula <- formula(inclinacion_peligrosa ~ altura +
                                                   diametro_tronco +
                                                   lat +
                                                   long + 
                                                   especie)
  
  for (i in 1:n){
    
  }

```

The models fit by, e.g., the lm and glm functions are specified in a compact symbolic form. The ~ operator is basic in the formation of such models. An expression of the form y ~ model is interpreted as a specification that the response y is modelled by a linear predictor specified symbolically by model. Such a model consists of a series of terms separated by + operators. The terms themselves consist of variable and factor names separated by : operators. Such a term is interpreted as the interaction of all the variables and factors appearing in the term.